Helpful Resources & Links

### 2024-06-06 index.qmd
update commit 6/6

>>>>

## Hosted Events
<div class="box">
**Student Organized Conferences**

1. 2024 LRES-PSPP Student Research Symposium  
    Role: Primary event organizer & co-emcee  
    Location: Montana State University, Bozeman, MT  
    Date: April 18, 2024  
    Hyperlink: [2024 Symposium](https://lres-research-symposium.weebly.com/?c=mkt_w_chnl:aff_geo:all_prtnr:sas_subprtnr:1538097_camp:brand_adtype:txtlnk_ag:weebly_lptype:hp_var:358504&sscid=61k8_2eb95&utm_source=ShareASale){target="_blank"}

2. 2023 LRES Colloquium  
    Role: Treasurer  
    Location: Montana State University, Bozeman, MT  
    Date: April 13, 2023

3. 2022 LRES Colloquium  
    Role: Treasurer  
    Location: Montana State University, Bozeman, MT  
    Date: April 29, 2022
</div>

### 2024-06-06 qmd/helpful.qmd
updated commit, done with paper 1 5/17/24
update commit 6/6

Below I have put many of the links that helped me.

@@

Watershed volunteering
https://youtu.be/65MAB0qRtAE?si=beO8jD5t5SOJzooF

>>>>

@@

## R Statistics
[Mixed Effects Models](https://meghan.rbind.io/blog/2022-06-28-a-beginners-guide-to-mixed-effects-models)

## Citations
I use quarto to generate my website reports. Here are a couple of resources to do the same.

- [Zotero Citations Repository](https://www.zotero.org/styles){target="_blank"}  
-

[Watershed volunteering](https://youtu.be/65MAB0qRtAE?si=beO8jD5t5SOJzooF){target="_blank"}
